Identifying regime transitions for water governance at a basin scale

### 2022-04-22 paper/sup/supplementary_information.tex
initialize standard to NW
fix(introduction,-abstract,-discussion,-method): polish paper according to the refree-1 from GEC
mainly: methods change, texts polishing

BREAKING CHANGE:

\title{Identifying regime transitions for water governance at a basin scale}
\author{Shuang Song, Shuai Wang, Xutong Wu, Yongping Wei, Graeme S. Cumming, Bojie Fu (complete author list)}
\correspondingauthor{Bojie Fu.\\E-mail: fubj@bnu.edu.cn}

@@

%% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text.
\SItext{This supplementary document consists of 5 \textit{Methods} sections, 9 \textit{SI Appendix} figures and 2 \textit{SI Appendix} tables. 
% 在方法S1部分，我们介绍了我们的研究区域——黄河流域及其区域划分。
In the section Methods S1, we introduced our study area, the Yellow River Basin, and its subdivisions of regions. 
% 在Methods S2部分，我们给出了使用的数据集的详细描述和分析它们的不确定性。
In the section Methods S2, we give a detailed description of used datasets and analysis their uncertainties. 
For the section Methods S3, we introduced how to harmonize different datasets with various spatial and temporal scales. 
Then, the indicators corresponding to the IWRU are introduced in the section Methods S4. 
Finally, we proposed sensitivity analysis in the section Methods S5, to test the robustness of our results.}

@@

Multiple types of dataset were used in this study (see Table S1). 
\subsection*{Statistical datasets}
% 使用了GDP数据，年鉴数据，还有从第二次水资源调查提取的数据
For statistics, we used GDP data, water resources uses data extracted from the 2nd National Water Resources Assessment Program \cite{zhouDecelerationChinaHuman2020} and statistical yearbook data of YRB \url{http://www.yrcc.gov.cn/other/hhgb/}. 
GDP data from the China Macro data in the Wind database, which firstly aggregated from annual reports of the provinces. Water resources use dataset was published by Zhou et al. \cite{zhouDecelerationChinaHuman2020}, which records water utilization in different sectors along with social-economic situations in perfects level. This dataset was mainly extracted by 2nd National Water Resources Assessment Program launched in 2002, led by the National Development and Reform Commission and the Ministry of Water Resources (see ref (1) and \url{http://www.mwr.gov.cn/english/publs/} for more details). Since then, the statistics from the survey using the same criteria have been supplemented and harmonized to the 2013 administrative divisions.

@@

\newpage
% 指数介绍
\section*{Methods S4. Indicators of IWRU}
% 水资源利用稳态指数考虑了流域尺度内人类利用水资源时最主要的三个维度，分别对应了 “有多少水”，“怎么用”和“给谁用”三个问题。
The Integrated Water Resources Utilization (IWRU) index of water resources utilization considers the three basic dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively (see Figure 1 in the main text). 
% 为了对这些维度进行量化，我们发现或发明了三个与指示其变化趋势相对应的指标:SFV指数、非供应共享和配置熵指标。
In order for these dimensions to be quantified, we used a total of three sub-indicators corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Allocation Entropy Metric.

@@

\subsection*{Priority: Non-provisioning share}
    %* 从消耗水 到 利用水
    % xxx等人通过考虑消费品中的水消耗提出了虚拟水理论，发现水资源作为粮食与消耗产品的供给是水资源的主要用途，且能够随着贸易发生流动。但随着水资源利用方式的变迁，在其基础上兴起的水足迹研究，则进一步泛化了水相关的产品和服务概念。如今，世界非产品形式供给于人类的水资源已达xx%，范围包含了xxxxxx等方式，人类社会发生着从“消耗水”向“利用水”的倾斜。
    How to use water resources?
    % 这里是一段关于虚拟水的介绍 
    % There has been put forward the virtual water theory by considering the water consumption in consumer goods, and found that the supply of water resources as food and consumption provisions is the main use of water resources, and can flow with trade. However, with the change of water resource utilization mode, the water footprint research on the basis of water footprint further generalizes the concept of water-related provisions and services. 
    % Today, the world's non-provisioning form of water supply to human beings are increasing more than 20 times faster growth, including industry, services and other ways, the human society is transformed from ``consumption of water'' to ``make use of water''.
    Here, we use Non-Provisioning Shares (NPS) of used water resources as a metric to indicate priority of water utility:
    $$ NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}} $$
    Where $i$ refers a certain region, or the whole basin, i.e:
	$I_P$ = $NPS_{basin}$
    %* 直接用水和非直接用水
    % 在本研究中，我们将牲畜用水、农村或城市的居民用水、农业用水认为是供给型用水。对应的，非供给性用水常常是工业用水，其中以能源用水为主。根据广泛的研究表明，水-粮食-能源之间存在广泛的联结，是水资源供应倾向性的一种体现，其中供给性用水常常是能够作为支持农产品生产的关键，而非供给水则更多参与了工业等社会过程。对中国整体而言，如果只考虑农业生产，中国是虚拟水贸易的流入国。但如果考虑工业耗水，中国则向外出口虚拟水资源。而黄河作为水资源高度稀缺的流域，更需要考虑两者之间的权衡，因此采用该比例作为指标能够简单、直接、有效地反映用水 priority 的变化。
    In this study, we consider water for livestock, water for rural or urban residents and water for agriculture as provisioning water. Correspondingly, non-provisioning water is often industrial water, mainly energy water. Extensive studies have shown that there is a wide connection between water, food and energy, which is a manifestation of water supply tendency, in which provisioning water is often the key to support the production of agricultural products, while non-provisioning water is more involved in industrial and other social processes. 
    % For China as a whole, if only agricultural production is considered, China is the recipient country of virtual water trade. But if industrial consumption is taken into account, China is exporting virtual water. However, as a river basin with high degree of water resource scarcity, the trade-off between the two has always been treated with greater value; thus, the adoption of this ratio as an indicator can simply, directly and effectively reflect the change of priority with water.

@@

Firstly, we performed three different normalization methods in construction of IWRU for breakpoint detection:

@@

Where $X$ is a time series and $X_{mean}$, $X_{std}$, $X_{min}$, $X_{max}$ are mean, standard deviation, minimum, maximum of it.
% 无论我们使用上述哪种标准化方法，将三个维度的指标合成为IWRU，我们对IWRU的断点检测结果都相同。
No matter which of the above standardized methods we use in combining the indicators of the three dimensions, and our detection results for IWRU breakpoints are the same.

@@

% \begin{figure}
% 	\centering
% 	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
% 	\caption{
% 		Changes in different dimensions of water resources utilization regimes and their main contributors.
% 		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
% 		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
% 		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
% 		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
% 		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
% 		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
% 		}
% 	\label{fig:dimensions}
% \end{figure}

@@

    % 表格
    \begin{tabular}{lrrrr}
    Dataset & Type & Spatial scale & Time limit & Source \\
    \midrule
    1. Water use & Statistical & Perfects & 1965-2013 & 2nd National Water Resources Assessment Program \\
    2. GDP & Statistical & Province & 1949-2019 & Wind database \\
    3. Groundwater and surface water use & Statistical & Watershed & 2003-2019 & Yearbooks of YRB by the YRCC. \\
    4. Reservoirs & Hydrological & Location & 1949-2015 & Wang et al. \cite{wangYellowRiverWater2019} \\
    5. Measured runoff & Hydrological & Location & 1949-2019 & Measured data from YRCC \\
    6. Laws & Political & Documents & 1949-2013 & YRCC \cite{yellowriverconservancycommissionYellowRiverBasin2013} \\
    7. History of YRCC & Political & Documents & 1949-2002 & YRCC \cite{ yellowriverarchivesOrganizationalHistoryYellow2004} \\
    \bottomrule
    \end{tabular}
\end{table}

@@

    \footnotesize{$^a$ If a policy was proposed by multiple legacies, we only choose the highest one to show.}
\end{table}

>>>>

\title{Identifying regime transitions for water governance at a basin scale}
\author{Shuang Song, Shuai Wang, Xutong Wu, Yongping Wei, Graeme S. Cumming, Bojie Fu (complete author list)}
\correspondingauthor{Bojie Fu.\\E-mail: bfu@rcees.ac.cn}

@@

%% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text.
\SItext{This supplementary document consists of 5 \textit{Methods} sections, 9 \textit{SI Appendix} figures and 2 \textit{SI Appendix} tables.
% 在方法S1部分，我们介绍了我们的研究区域——黄河流域及其区域划分。
In the section Methods S1, we introduced our study area, the Yellow River Basin, and its subdivisions of regions.
% 在Methods S2部分，我们给出了使用的数据集的详细描述和分析它们的不确定性。
In the section Methods S2, we give a detailed description of used datasets and analysis their uncertainties.
For the section Methods S3, we introduced how to harmonize different datasets with various spatial and temporal scales.
Then, the indicators corresponding to the IWGI are introduced in the section Methods S4.
Finally, we proposed sensitivity analysis in the section Methods S5, to test the robustness of our results.}

@@

Multiple types of dataset were used in this study (see Table S1).
\subsection*{Statistical datasets}
% 使用了GDP数据，年鉴数据，还有从第二次水资源调查提取的数据
For statistics, we used GDP data, water resources uses data extracted from the 2nd National Water Resources Assessment Program \cite{zhouDecelerationChinaHuman2020} and statistical yearbook data of YRB \url{http://www.yrcc.gov.cn/other/hhgb/}.
GDP data from the China Macro data in the Wind database, which firstly aggregated from annual reports of the provinces. Water resources use dataset was published by Zhou et al. \cite{zhouDecelerationChinaHuman2020}, which records water utilization in different sectors along with social-economic situations in Prefectures level. This dataset was mainly extracted by 2nd National Water Resources Assessment Program launched in 2002, led by the National Development and Reform Commission and the Ministry of Water Resources (see ref (1) and \url{http://www.mwr.gov.cn/english/publs/} for more details). Since then, the statistics from the survey using the same criteria have been supplemented and harmonized to the 2013 administrative divisions.

@@

\newpage
% 指数介绍
\section*{Methods S4. Indicators of IWGI}
% 水资源利用稳态指数考虑了流域尺度内人类利用水资源时最主要的三个维度，分别对应了 “有多少水”，“怎么用”和“给谁用”三个问题。
The Integrated Water Governance Index (IWGI) of water resources utilization considers the three basic dimensions of human utilization of water resources at the watershed scale, corresponding to the three questions of ``how much water'', ``how to use'' and ``for whom, for where'' respectively (see Figure 1 in the main text).
% 为了对这些维度进行量化，我们发现或发明了三个与指示其变化趋势相对应的指标:SFV指数、非供应共享和配置熵指标。
In order for these dimensions to be quantified, we used a total of three sub-indicators corresponding to the trend indicating their change: SFV Index, Non-provisioning Share and Allocation Entropy Metric.

@@

\subsection*{Purpose: Non-provisioning share}
    %* 从消耗水 到 利用水
    % xxx等人通过考虑消费品中的水消耗提出了虚拟水理论，发现水资源作为粮食与消耗产品的供给是水资源的主要用途，且能够随着贸易发生流动。但随着水资源利用方式的变迁，在其基础上兴起的水足迹研究，则进一步泛化了水相关的产品和服务概念。如今，世界非产品形式供给于人类的水资源已达xx%，范围包含了xxxxxx等方式，人类社会发生着从“消耗水”向“利用水”的倾斜。
    How to use water resources?
    % 这里是一段关于虚拟水的介绍
    % There has been put forward the virtual water theory by considering the water consumption in consumer goods, and found that the supply of water resources as food and consumption provisions is the main use of water resources, and can flow with trade. However, with the change of water resource utilization mode, the water footprint research on the basis of water footprint further generalizes the concept of water-related provisions and services.
    % Today, the world's non-provisioning form of water supply to human beings are increasing more than 20 times faster growth, including industry, services and other ways, the human society is transformed from ``consumption of water'' to ``make use of water''.
    Here, we use Non-Provisioning Shares (NPS) of used water resources as a metric to indicate purpose of water utility:
    $$ NPS_{i} = \frac{WU_{non-pro, i}}{WU_{pro, i} + WU_{non-pro, i}} $$
    Where $i$ refers a certain region, or the whole basin, i.e:
	$I_P$ = $NPS_{basin}$
    %* 直接用水和非直接用水
    % 在本研究中，我们将牲畜用水、农村或城市的居民用水、农业用水认为是供给型用水。对应的，非供给性用水常常是工业用水，其中以能源用水为主。根据广泛的研究表明，水-粮食-能源之间存在广泛的联结，是水资源供应倾向性的一种体现，其中供给性用水常常是能够作为支持农产品生产的关键，而非供给水则更多参与了工业等社会过程。对中国整体而言，如果只考虑农业生产，中国是虚拟水贸易的流入国。但如果考虑工业耗水，中国则向外出口虚拟水资源。而黄河作为水资源高度稀缺的流域，更需要考虑两者之间的权衡，因此采用该比例作为指标能够简单、直接、有效地反映用水 purpose 的变化。
    In this study, we consider water for livestock, water for rural or urban residents and water for agriculture as provisioning water. Correspondingly, non-provisioning water is often industrial water, mainly energy water. Extensive studies have shown that there is a wide connection between water, food and energy, which is a manifestation of water supply tendency, in which provisioning water is often the key to support the production of agricultural products, while non-provisioning water is more involved in industrial and other social processes.
    % For China as a whole, if only agricultural production is considered, China is the recipient country of virtual water trade. But if industrial consumption is taken into account, China is exporting virtual water. However, as a river basin with high degree of water resource scarcity, the trade-off between the two has always been treated with greater value; thus, the adoption of this ratio as an indicator can simply, directly and effectively reflect the change of purpose with water.

@@

Firstly, we performed three different normalization methods in construction of IWGI for breakpoint detection:

@@

Where $X$ is a time series and $X_{mean}$, $X_{std}$, $X_{min}$, $X_{max}$ are mean, standard deviation, minimum, maximum of it.
% 无论我们使用上述哪种标准化方法，将三个维度的指标合成为IWGI，我们对IWGI的断点检测结果都相同。
No matter which of the above standardized methods we use in combining the indicators of the three dimensions, and our detection results for IWGI breakpoints are the same.

@@

% \begin{figure}
% 	\centering
% 	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
% 	\caption{
% 		Changes in different dimensions of water resources utilization regimes and their main contributors.
% 		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
% 		\textbf{B,} changes of water utilization purpose, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
% 		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
% 		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
% 		\textbf{E,} Main impact water uses to water utilization purpose, and their change contributions to non-provisioning water shares.
% 		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
% 		}
% 	\label{fig:dimensions}
% \end{figure}

@@

    % 表格
    \begin{tabular}{lrrrr}
    Dataset & Type & Spatial scale & Time limit & Source \\
    \midrule
    1. Water use & Statistical & Prefectures & 1965-2013 & 2nd National Water Resources Assessment Program \\
    2. GDP & Statistical & Province & 1949-2019 & Wind database \\
    3. Groundwater and surface water use & Statistical & Watershed & 2003-2019 & Yearbooks of YRB by the YRCC. \\
    4. Reservoirs & Hydrological & Location & 1949-2015 & Wang et al. \cite{wangYellowRiverWater2019} \\
    5. Measured runoff & Hydrological & Location & 1949-2019 & Measured data from YRCC \\
    6. Laws & Political & Documents & 1949-2013 & YRCC \cite{yellowriverconservancycommissionYellowRiverBasin2013} \\
    7. History of YRCC & Political & Documents & 1949-2002 & YRCC \cite{ yellowriverarchivesOrganizationalHistoryYellow2004} \\
    \bottomrule
    \end{tabular}
\end{table}

@@

    \footnotesize{$^a$ If a policy was proposed by multiple legacies, we only show the highest one.}
\end{table}
